\textbf{Automated Reasoning\\Practical Assignment -- Part 1}

### 2022-10-10 docs/paper.tex
[Dinner] write report

\documentclass{scrartcl}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{minted}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{svg}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{scalerel}

\usepackage{amsfonts}

@@

>>>>

\documentclass{scrartcl}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage{minted}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{svg}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{scalerel}
\usepackage{amsfonts}

@@

\subsection{Variables} % (fold)
\label{sub:dinner_variables}
We use the following terminology:
\begin{itemize}
	\item A \textbf{person} indicates a single person.
	\item A \textbf{house} indicates a place where people dine together.
	\item A \textbf{round} indicates a single day at which people dine together.
	\item A \textbf{group} indicates a group that eats in the same house on the same day.
\end{itemize}
With $p\in h$ we will denote that person $p$ lives in house $h$.\\
With $g\in r$ we will denote that group $g$ dines during round $r$.\\

We use the following variables:\\
\begin{tabular}{ll}
	$\mathtt{inGroup}_{gp}$ & true when person $p$ dines with group $g$.\\
	$\mathtt{groupHost}_{gh}$ & true when group $g$ dines at house $h$.\\
\end{tabular}

% subsection dinner_variables (end)

\subsection{Constraints} % (fold)
\label{sub:dinner_constraints}
We have a lot of constraints that reference how many statements are true.\\
We will use the following shorthand: $\sum_i S(i)$\\
This denotes the number of true statements among the statements $S(i)$.
\begin{itemize}
	\item Due to the 1.5 meter restriction in every house at most 5 people may be present.\\
	We add the following constraint for every group $g$:
	$$\sum_{p}\mathtt{inGroup}_{gp}\leq 5$$
	\item \ldots by which every round has to be prepared and served in two houses simultaneously, each with the corresponding couple and three guests.\\
	This states, with a lot of words, that all $10$ people dine each round.\\
	We add the following constraint for each round $r$ and person $p$:
	$$\sum_{g\in r}\mathtt{inGroup}_{gp}\geq 1$$
	\item \ldots each with the corresponding couple \ldots\\
	This means that the owners of a house must be present at a dinner in their house.\\
	We add the following constraint for each group $g$, house $h$ and person $p\in h$:
	$$\mathtt{groupHost}_{gh}\to\mathtt{inGroup}_{gp}$$
	Additionally it states that each group must be hosted by exactly one couple.
	We add the following constraint for each group $g$:
	$$\sum_h\mathtt{groupHost}_{gh} = 1$$
	\item Every couple will serve two rounds in their house.\\
	We add the following constraint for each house $h$:\\
	$$\sum_g\mathtt{groupHost_{gh}}\geq 2$$
	\item Every two people among the 10 participants meet each other at most 4 times during these 5 rounds.\\
	We add the following constraint for every pair of persons $p_1<p_2$:\\
	$$\sum_g(\mathtt{inGroup}_{gp_1}\land\mathtt{inGroup}_{gp_2})\leq 4$$
\subsection{Optional constraints} % (fold)
\label{sub:dinner_optional_constraints}
\begin{enumerate}[label=\Alph*)]
	\item Every two people among the 10 participants meet each other at least once.\\
	We add the following constraint for every pair of persons $p_1<p_2$:
	$$\sum_g(\mathtt{inGroup}_{gp_1}\land\mathtt{inGroup}_{gp_2})\geq 1$$
	\item Every two people among the 10 participants meet each other at most $3$ times.\\
	We add the following constraint for every pair of persons $p_1<p_2$:
	$$\sum_g(\mathtt{inGroup}_{gp_1}\land\mathtt{inGroup}_{gp_2})\leq 3$$
	\item Couples never meet outside their own houses\\
	We add the following constraint for every group $g$ and house $h$:
	$$\mathtt{groupHost}_{gh}\lor\sum_{p\in h}\mathtt{inGroup}_{pg}\leq 1$$
	If a couple does not host a group there is at most one person of the couple in that group. Therefore they do not meet in that group.
	\item For every house the six guests are distinct.\\
	This is the case exactly when each house hosts each person at most once.
	We add the following constraint for every house $h$ and person $p\notin h$:
	$$\sum_{g}(\mathtt{groupHost}_{gh}\land \mathtt{inGroup}_{pg})\leq 1$$
\end{enumerate}
% subsection dinner_optional_constraints (end)

\subsection{Results} % (fold)
\label{sub:dinner_results}
We have run Z3 for every subset of additional constraints with the standard constraints.
We have noticed that Z3 takes too long to decide the cases where constraints A and B are both required.\\
The only combination that was proven to be unsatisfiable was $A,C,D$. This implies that the combination of $A,B,C,D$ is also unsatisfiable.\\
All remaining subsets are satisfiable.\\

\begin{tabular}{ll|llll}
\multicolumn{2}{l|}{} & & & A & A \\
\multicolumn{2}{l|}{\multirow{-2}{*}{Constraints}} & & B & & B \\ \hline
 & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{yellow!50}UNKNOWN \\
 & D & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{yellow!50}UNKNOWN \\
C & & \cellcolor{green!50}SAT & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{yellow!50}UNKNOWN \\
C & D & \cellcolor{green!50}SAT & \cellcolor{green!50}\textbf{SAT} & \cellcolor{red!50}UNSAT & \cellcolor{red!50}UNSAT 
\end{tabular}

Here are solutions to the bold subsets that imply satisfiability of all green subsets:\\

\begin{tabular}{l|ll|lll|ll|lll}
B,C,D & \multicolumn{5}{l|}{House 1} & \multicolumn{5}{l}{House 2} \\
Round & \multicolumn{2}{l}{Host} & \multicolumn{3}{l|}{Guest} & \multicolumn{2}{l}{Host} & \multicolumn{3}{l}{Guest} \\ \hline
1 & 0 & 1 & 3 & 5 & 9 & 6 & 7 & 2 & 4 & 8 \\
2 & 0 & 1 & 2 & 4 & 6 & 8 & 9 & 3 & 5 & 7 \\
3 & 2 & 3 & 0 & 6 & 8 & 4 & 5 & 1 & 7 & 9 \\
4 & 2 & 3 & 1 & 7 & 9 & 4 & 5 & 0 & 6 & 8 \\
5 & 6 & 7 & 1 & 3 & 5 & 8 & 9 & 0 & 2 & 4 \\
\end{tabular}

\begin{tabular}{l|ll|lll|ll|lll}
A,C & \multicolumn{5}{l|}{House 1} & \multicolumn{5}{l}{House 2} \\
Round & \multicolumn{2}{l}{Host} & \multicolumn{3}{l|}{Guest} & \multicolumn{2}{l}{Host} & \multicolumn{3}{l}{Guest} \\ \hline
1 & 0 & 1 & 2 & 5 & 9 & 6 & 7 & 3 & 4 & 8 \\
2 & 0 & 1 & 3 & 5 & 6 & 8 & 9 & 2 & 4 & 7 \\
3 & 2 & 3 & 0 & 5 & 7 & 8 & 9 & 1 & 4 & 6 \\
4 & 2 & 3 & 1 & 7 & 9 & 4 & 5 & 0 & 6 & 8 \\
5 & 4 & 5 & 1 & 3 & 9 & 6 & 7 & 0 & 2 & 8 \\
\end{tabular}

\begin{tabular}{l|ll|lll|ll|lll}
A,D & \multicolumn{5}{l|}{House 1} & \multicolumn{5}{l}{House 2} \\
Round & \multicolumn{2}{l}{Host} & \multicolumn{3}{l|}{Guest} & \multicolumn{2}{l}{Host} & \multicolumn{3}{l}{Guest} \\ \hline
1 & 0 & 1 & 6 & 7 & 9 & 2 & 3 & 4 & 5 & 8 \\
2 & 0 & 1 & 2 & 4 & 8 & 6 & 7 & 3 & 5 & 9 \\
3 & 2 & 3 & 0 & 1 & 6 & 4 & 5 & 7 & 8 & 9 \\
4 & 4 & 5 & 0 & 1 & 3 & 8 & 9 & 2 & 6 & 7 \\
5 & 6 & 7 & 0 & 2 & 4 & 8 & 9 & 1 & 3 & 5 \\
\end{tabular}
% subsection dinner_results (end)

\end{itemize}
% subsection dinner_constraints (end)
